Effects of sexual selection on non-sexual fitness components: a meta-analysis

### 2018-05-24 meta_analysis_sexual_selection_pop_fitness.Rmd
Justin Previous Bayesian Explore

**Table S8** The predictions in the plot above use the following dataframe
```{r}
colnames(predictions.complete2) <- c("Sex", "Environment", "Prediction", "SE", "CI.lb", "CI.ub", "n")
predictions.complete2 <- format(predictions.complete2, digits = 2)
predictions.complete2 %>% pander()
```

@@

We can run a bayesian model using the brms package. The model has the same moderators as the REML approach used above. 
```{r, warning=FALSE, message = FALSE}
library(rstan) #Note that installation requires some effort
library(brms) 
library(backports) #seems to be a dependency
devtools::install_github("mvuorre/brmstools")
library(brmstools) 
```

```{r, warning = FALSE, results='hide', message=FALSE}
#Use brm to create a model similar to the one used in the REML approach. 
#Use brm to create a model similar to the one used in the REML approach. 
meta.brms <- brm(g| se(sqrt(var.g), sigma = TRUE)  ~ 1 + Sex * Environment #response is Hedges' g and the standard error associated with it (sqrt(var.g)) with sex and environment as moderators
                + (1|Study.ID) #group level effect #1
                + (1|Outcome), #group level effect #2 (unrelated/crossed) with #1
                family = "gaussian", #default
                seed = 1,
                cores = 4, chains = 4, iter = 4000, #Run 4 chains in parrallel for 4000 iterations (2000 are burn in)
                control = list(adapt_delta = 0.99),
                data = restricted.data)
```

@@

```{r, fig.height=5, fig.width=5}

pd <- position_dodgev(height = 0.3)
posterior.plot <- posterior_fit %>% ggplot()+
  geom_density_ridges(aes(x=value, y = Environment, fill = Sex), alpha = 0.4, scale = 0.6, position = position_nudge(y = 0.15), height = 10)+
  geom_vline(xintercept = 0, linetype = 2, colour = "black") + 
    ylab("Environment\n")+
  xlab("\nPosterior Effect Size (Hedges' g)")+
  scale_fill_brewer(palette = "Set1")+
  scale_color_brewer(palette = "Set1")+
  guides(fill = guide_legend(reverse=T, override.aes = list(size = 0.5)))+
  scale_x_continuous(limits = c(-0.5, 1.2), breaks = c(-1, -.5, 0, 0.5, 1))+

@@

  theme(panel.spacing = unit(0.1, "lines"),
        text = element_text(size=14),
        panel.border= element_blank(),
        axis.line=element_line(), 
        panel.grid.major.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        panel.grid.minor.x = element_blank(), 
        legend.text = element_text(size=14), 
        legend.title=element_text(size=14, 
                                  face = "bold"),
        axis.title.x = element_text(hjust = 0.5, size = 14),
        axis.title.y = element_text(size = 14),
        axis.text.y = element_text(angle = 0),
        plot.title = element_text(size = 14))

both.plots <- posterior.plot + 
  geom_point(data = predictions.complete2, 
             aes(x = pred, y = Environment, size=nn, fill = Sex), 
             shape=21, color = "grey20", position = pd, show.legend = F) +

  geom_errorbarh(data = predictions.complete2, 
                 aes(x= pred, xmin = predictions.complete2$ci.lb,
                     xmax = predictions.complete2$ci.ub, y = Environment,
                     color = Sex), 
                 height = 0, show.legend = F, position = pd)+
    scale_y_discrete(expand=c(0.075,0))

@@

svg("figures/both_plot.svg", width=6, height=6)
both.plots
dev.off()
```
<br></br>
**Figure X** Posterior fitted values for Hedges' g using the same model as above

>>>>

**Table S8** The predictions in the plot above use the following dataframe
```{r}
colnames(predictions.complete2) <- c("Sex", "Environment", "Prediction", "SE", "CI.lb", "CI.ub", "n")
predictions.complete2 <- format(predictions.complete2, digits = 2)
predictions.complete2$Prediction = as.numeric(predictions.complete2$Prediction)
predictions.complete2$CI.lb = as.numeric(predictions.complete2$CI.lb)
predictions.complete2$CI.ub = as.numeric(predictions.complete2$CI.ub)
predictions.complete2$n = as.numeric(predictions.complete2$n)

predictions.complete2 %>% pander()
```

@@

We can run a bayesian model using the brms package. The model has the same moderators as the REML approach used above. 
```{r, warning=FALSE, message = FALSE}
library(rstan) #Note that installation requires some effort
library(brms) 
library(backports) #seems to be a dependency
#devtools::install_github("mvuorre/brmstools")
library(brmstools) 
```

```{r, warning = FALSE, results='hide', message=FALSE}
#Use brm to create a model similar to the one used in the REML approach. 
#Use brm to create a model similar to the one used in the REML approach. 
meta.brms <- brm(g| se(sqrt(var.g), sigma = TRUE)  ~ 1 + Sex * Environment #response is Hedges' g and the standard error associated with it (sqrt(var.g)) with sex, environment and their interaction as moderators
                + (1|Study.ID) #group level effect #1
                + (1|Outcome), #group level effect #2 (unrelated/crossed) with #1
                family = "gaussian", #default
                seed = 1,
                cores = 4, chains = 4, iter = 4000, #Run 4 chains in parrallel for 4000 iterations (2000 are burn in)
                control = list(adapt_delta = 0.99),
                data = restricted.data)
```

@@

```{r, fig.height=5.5, fig.width=5.5}

pd <- position_dodgev(height = 0.3)
posterior.plot <- posterior_fit %>% ggplot()+
  geom_density_ridges(aes(x=value, y = Environment, fill = Sex), alpha = 0.4, scale = 0.6, position = position_nudge(y = 0.15), height = 10, show.legend = F)+
  geom_vline(xintercept = 0, linetype = 2, colour = "black") + 
    ylab("Environment")+
  xlab("\nEffect Size (Hedges' g)")+
  scale_fill_brewer(palette = "Set1")+
  scale_color_brewer(palette = "Set1")+
  scale_x_continuous(limits = c(-0.5, 1.2), breaks = c(-1, -.5, 0, 0.5, 1))+

@@

  theme(panel.spacing = unit(0.1, "lines"),
        text = element_text(size=16),
        panel.border= element_blank(),
        axis.line=element_line(), 
        panel.grid.major.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        panel.grid.minor.x = element_blank(), 
        legend.text = element_text(size=16), 
        legend.title=element_text(size=16, 
                                  face = "bold"),
        axis.title.x = element_text(hjust = 0.5, size = 14),
        axis.title.y = element_text(size = 16, hjust = 0.35, margin = margin(r=-10)),
        axis.text.y = element_text(angle = 0),
        plot.title = element_text(size = 16))

both.plots <- posterior.plot + 
  geom_point(data = predictions.complete2, 
             aes(x = Prediction, y = Environment, size=n, fill = Sex), 
             shape=21, color = "grey20", position = pd) +

    guides(fill = guide_legend(reverse=T, override.aes = list(size = 7.5)))+
    scale_size(guide = 'none')+

  geom_errorbarh(data = predictions.complete2, 
                 aes(x= Prediction, xmin = predictions.complete2$CI.lb,
                     xmax = predictions.complete2$CI.ub, y = Environment,
                     color = Sex), 
                 height = 0, show.legend = F, position = pd)+
    scale_y_discrete(expand=c(0.075,0))

@@

# svg("figures/both_plot.svg", width=5.5, height=5.5)
# both.plots
# dev.off()
# 
# pdf("figures/both_plot.pdf",  width = 5.5, height = 5.5)
# both.plots
# dev.off()
```
<br></br>
**Figure X** Posterior fitted values for Hedges' g using the same model as above
